On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-30 paper/paper.tex
Briefly tie the C backend back to the rest of the transformation system using a previously mentioned example

See Appendix A for more implementation details of \ttt{absEnv}.

@@

>>>>

See Appendix A for implementation details of \ttt{absEnv}.

@@

A C code generation function \ttt{genC} is implemented

\begin{lstlisting}
genC :: E a -> String
...
\end{lstlisting}

To use this, for example, with the previously mentioned \ttt{isEven} implementation we
can write:

\begin{lstlisting}
isEvenE :: E (Int -> Bool)
isEvenE =
  externalize (
    case x == 0 of
      True -> True
      False ->
        case x == 1 of
          True -> False
          False -> isEvenE (x - 2))

isEvenC :: String
isEvenC = genC isEvenE
\end{lstlisting}
